%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt]{report} 
\usepackage[a4paper, margin=2.5cm]{geometry} %set up margins 2.5cm
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.5}  % increase line spacing
\usepackage{fontspec}
\setmainfont{Arial}
% MS Word style justification rather than latex-style hyphenation
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000
%%%%%% Figures 
\usepackage{graphicx} % for graphics
\usepackage{float} % to position graphics
\usepackage[labelfont=bf]{caption} 
\captionsetup[figure]{font={stretch=1.2}}    %% change 1.2 as you like
\usepackage[raggedright]{titlesec} %raggedright option = don't cut titles!
\usepackage{xcolor}
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39} %citations color
\usepackage[hyphens]{url}
\usepackage{hyperref}%for DOI
%\usepackage[url]
\hypersetup{colorlinks,linkcolor=black,urlcolor=teal,citecolor=teal} 
\setlength{\parindent}{0pt} % no paragraph indentation
\setlength{\parskip}{1em} %but a space
\usepackage{textcomp} % provides underscore
\usepackage{titletoc}% format TOC titles
\titlecontents{chapter}% <section-type>
  [0pt]% <left>
  {\bfseries}% <above-code>
  {\chaptername\ \thecontentslabel:\quad}% <numbered-entry-format>
  {}% <numberless-entry-format>
  {\hfill\contentspage}% <filler-page-format>
  
\usepackage{titlesec} % format chapters titles
\titleformat{\chapter}[display]
            {\normalfont\LARGE\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\LARGE}[\vspace{2ex}\titlerule]
%per chapter numbering of tables and figures
\usepackage{chngcntr}
\counterwithin{figure}{chapter}
% mathematical equations
\usepackage{upgreek} % greek letters not in italic upalpha etc.
\usepackage{mathtools}
\numberwithin{equation}{section} % how the equation numbers are formed
\newtagform{show_eq}{(Eq.\ }{)}  % how the equation numbers are displayed
\usetagform{show_eq}
\usepackage{chngcntr} %Sequential equation numbering when using 'report' class
\counterwithout{equation}{chapter}
%bibliography:
\input{biblisettings.tex}
\bibliography{mybib280520.bib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input{chapters/titlepage}
\clearpage
\input{chapters/p2}
\clearpage

\pagenumbering{arabic} % start numbering from then on

\tableofcontents

\chapter*{List of abbreviations}
\addcontentsline{toc}{chapter}{List of abbreviations}
\begin{tabular}{l l}
Abbreviation & full term \\
\hline
AIC & Akaike information criterion \\
CI & confidence interval \\
Ct & cycle threshold \\
°C & degrees celsius \\
DNA & deoxyribonucleic acid \\
dpi & days post infection \\
F1 & first generation of crossing \\
F2 & second generation of crossing \\
F3 & third generation of crossing \\
F4 & fourth generation of crossing \\
Fig & figure \\
GTP & guanosine triphosphate \\
He & expected heterozygosity \\
HI & hybrid index \\
HMHZ   & European house mouse hybrid zone \\
IFNγ & interferon γ \\
km & kilometer \\
log2 & logarithm to the base 2 \\
MHC & major histocompatibility complex \\
min & minute \\
Mmd & \textit{Mus musculus domesticus} \\
Mmm    & \textit{Mus musculus musculus}  \\
mL & milliliter
\end{tabular}

\newpage

\begin{tabular}{l l}
Abbreviation & full term \\
\hline
NaCl & sodium chloride \\
OPG & oocysts per gram of feces \\
PCR & polymerase chain reaction \\
qPCR & quantitative polymerase chain reaction \\
s & second \\
sd & standard deviation \\
SIR & susceptible, infected, removed \\
Th1 & T helper type 1 \\
Th2 & T helper type 2 \\
ZINB &  zero-inflated negative binomial
\end{tabular}

\chapter{General introduction}
\input{chapters/1introduction}
 
\chapter{Intensity of infection with intracellular \textit{Eimeria spp.} and pinworms is reduced in hybrid mice compared to parental subspecies}
\input{chapters/2article1}

\chapter{Coupling between tolerance and resistance differs between related \textit{Eimeria} parasite species: implications for coevolution with their mouse hosts}
\input{chapters/3article2}

\chapter{General discussion}
\input{chapters/4discussion}

\chapter*{Summary}
\addcontentsline{toc}{chapter}{Summary}
\input{chapters/Summary}

\chapter*{Zusammenfassung}
\addcontentsline{toc}{chapter}{Zusammenfassung}
\input{chapters/Zusammenfassung}

\newpage
\printbibliography[heading=bibintoc]

\chapter*{Supplementary figures}
\addcontentsline{toc}{chapter}{Supplementary figures}
\input{chapters/supplementaryFigures}

\chapter*{List of publications}
\addcontentsline{toc}{chapter}{List of publications}
\input{chapters/publications}

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\input{chapters/Acknowledgements}

\newpage

\section*{Funding sources}
\addcontentsline{toc}{chapter}{Funding source}

The work presented in this thesis was funded by the German Research Foundation (DFG) Grant [HE 7320/1-1] to Emanuel Heitlinger. V{\'{\i}}ctor Hugo Jarqu{\'{\i}}n-D{\'{\i}}az is an associated student of Research Training Group GRK 2046 funded by the DFG. Mouse genotyping was carried out as a part of the Czech Science Foundation projects No. 15-13265S and 16-23773S (to Stuart J. E. Baird, Milo{\v{s}} Machol{\'{a}}n and Jaroslav Pi{\'{a}}lek). The maintenance of wild-derived strains was supported by the ROSE program from Czech Academy of Sciences and the Czech Science Foundation (project 16-23773S) to Jaroslav Pi{\'{a}}lek.

\section*{Interessenskonflikte}
\addcontentsline{toc}{chapter}{Interessenskonflikte}

Es besteht kein Interessenskonflikt durch finanzielle Unterstützung der Arbeiten.

\section*{Selbstständigkeitserklärung}
\addcontentsline{toc}{chapter}{Selbstständigkeitserklärung}

Hiermit bestätige ich, dass ich die vorliegende Arbeit selbständig angefertigt habe. Ich versichere, dass ich ausschließlich die angegebenen Quellen und Hilfen in Anspruch genommen habe.
\par
Berlin, 21. May 2020 \hfill Alice Christiane Anne-Marie Balard

\end{document}
