I want to thank all the people that supported me during these past years and that helped make the present thesis possible.\par

First, I would like to thank my supervisor Emanuel Heitlinger. Emanuel, being your studen was challenging and exhausting, and I am deeply grateful for that: I learned so much from you these years. Thank you for transmitting your passion for science with neverending magnanimity, and for creating such a supportive and joyful team. You listen and respect the opinion of every of your students, it's always possible to discuss with you, you prioritise science over politics, which are rare qualities in science. I am deeply thankful for having had you as my PhD supervisor.\par

My sincere gratitude goes to Heribert Hofer, Justyna Wolinska and January Weiner, members of my thesis advisory committee, that supported me and helped improving this project all along its course.\par

Victor, my PhD-brother, counting you as a colleague and friend is a wonderful chance. Thank you so much for your support all these years, for your heart of gold, for your intelligence and for your Buddha-wisdom. I wish you all the best for your carreer and life, and hope we will have the chance to collaborate in the future. Jenny, my PhD-sister (yes, you were a PhD undercover all these years, stop denying), thank you for your joy, for your unconditional support, for having accepted to sing "Ring of fire" ON STAGE with me. Guys, looking forward to go to a conference together wearing flip-flops and hawaiian shirts in some years.\par

I want to thank my other adorable fellow PhD students Laura, Parnika \& Luke, as well as the students I had the chance to supervise and learn from, Vivian, Franci, Mert, and the others I did not supervise directly, Tabea, Yasmin, Julia, Svenia,... it was a pleasure to have you as my minions, I hope I didn't traumatise you too much. I would like to thank my colleagues and friends from HU molpara, especially Oriana, Florence and our (short-lived) journal club, and Calvin that helped us releasing the tensions by teaching us how to hit each other in the face and pretend it was to learn boxing. Also my collaborators from Czech, especially Iva \& Ludo for your kind heart and motivation during the numerous field trips, thanks to you these hard working days had a taste of summer camp. I'll keep a special place in my heart for these beautiful campfires and songs we shared.\par

To my friends, thanks for your support. In particular: \par
Charlotte, you know I don't believe in soul mate, prince charming and all this patriarchic bullsh**, but I am sure if little girls were told the truth, i.e. that if you are very very lucky you'll find a friend that understands you, supports you, challenges you, surprises you, makes you laugh quasi non-stop for at least a decade (and hopefully for the next bunch of decades to come), the world would be a better place. I am so grateful to count you as my friend. A very wise woman once wrote: "\textit{Knowing that I have you makes me reach such a high level of mental well-being}". Thanks for being always there, puppet master.\par
To my fairies: Francesca, thank you for being so passionate, warm, supportive, thank you for making me love reagaeton, I love you to the moon and back, I'll join you soon and we'll rock London together. Susana, little sister, thank you for your friendship and trust, for being always ready to talk about statistics and feminism, for having watched the extended edition of the Lord of the Rings with me all night without (almost) complaining, I love you and I'll kick ass for you any time.\par
Totta, my elfish role model, thanks for your friendship, for not having named any of your kids Legolas or Galadriel despite my insistence, thanks for always being critical and challenging my ideas, making me a better scientist. Also, thanks for having mentionned four years ago that your boss was looking for a PhD student for a position in which I would fit very well, here is the >100 pages proof that you were right!\par
Masha, thanks for providing me with a cocoon in Berlin, you were my first and last roomate in this city, thanks for your support, for accepting without blinking to discuss so much about parasites when I needed an external ear, and for the warmth of your friendship.\par

To my family, thanks for your love and support. Papa, thanks for having given me this curiosity that is so intense that I made it a carreer, for supporting me constantly, for giving me so much love and security that I feel like I could climb mountains any day, you're the best dad possible, statistically speaking with a very very very low p-value; I love you. Pierre, my twin, you are basically the best person, there is not enough words to tell you how much I love you, so I'll rather tell you that when we buy this pinball machine, you can chose the design. Kiko, I love you, thanks for your love and support all these years, so many times you told me "tête dans le guidon!!" when it was hard, but also recomforting words when it was needed, I would not be there without you, thanks a thousand times.
