\textbf{Published}: 
\par
\textbf{Alice Balard}, Víctor Hugo Jarquín-Díaz, Jenny Jost, Iva Martincová, Ľudovít Ďureje, Jaroslav Piálek, Miloš Macholán, Joëlle Goüy de Bellocq, Stuart J. E. Baird, Emanuel Heitlinger (2020). Intensity of infection with intracellular \textit{Eimeria} spp. and pinworms is reduced in hybrid mice compared to parental subspecies. \textit{Journal of Evolutionary Biology} doi:\url{https://doi.org/10.1111/jeb.13578}
\par
Víctor Hugo Jarquín-Díaz, \textbf{Alice Balard}, Jenny Jost, Julia Kraft, Mert Naci Dikmen, Jana Kvičerová, Emanuel Heitlinger (2019). Detection and quantification of house mouse \textit{Eimeria} at the species level – Challenges and solutions for the assessment of coccidia in wildlife. \textit{International Journal for Parasitology: Parasites and Wildlife}. doi:\url{https://doi.org/10.1016/j.ijppaw.2019.07.004}
\par
Víctor Hugo Jarquín-Díaz, \textbf{Alice Balard}, Anna Mácová, Jenny Jost, Tabea Roth von Szepesbéla, Karin Berktold, Steffen Tank, Jana Kvičerová, Emanuel Heitlinger (2020). Generalist \textit{Eimeria} species in rodents: Multilocus analyses indicate inadequate resolution of established markers. \textit{Ecology and Evolution}. doi:\url{https://doi.org/10.1002/ece3.5992}
\par
\textbf{Submitted}:
\par
\textbf{Alice Balard}, Víctor Hugo Jarquín-Díaz, Jenny Jost, Vivian Mittné, Francisca Böhning, Ľudovít Ďureje, Jaroslav Piálek, Emanuel Heitlinger. Coupling between tolerance and resistance differs between related \textit{Eimeria} parasite species: implications for coevolution with their mouse hosts. Submitted to \textit{Journal of Evolutionary Biology}

